---
title: "trialforgeR Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{trialforgeR Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(trialforgeR)
```

The `trialforgeR` package provides lightweight, spec-driven validation utilities
for synthetic clinical datasets. This vignette demonstrates how to evaluate the
packaged sample data against the bundled specification.

```{r load-samples}
data_files <- list(
  sdtm_dm = system.file("extdata/sample_data/sdtm_dm.csv", package = "trialforgeR"),
  sdtm_ae = system.file("extdata/sample_data/sdtm_ae.csv", package = "trialforgeR"),
  adam_adae = system.file("extdata/sample_data/adam_adae.csv", package = "trialforgeR")
)

results <- trialforge_validate(data_files)
head(results)
```

```{r summary}
summary_results <- dplyr::count(results, status)
summary_results
```

You can also generate an HTML QC report directly.

```{r eval=FALSE}
report_path <- generate_qc_report(results, out_file = "qc_report.html")
report_path
```

The same validation engine powers the Shiny app and CLI interface included with
this package, supporting both interactive and automated workflows.
